### 2017-03-30 paper/evaluation.tex
pending some updates... vpn issues here

% considered all projects classified as \medg{} and \longg{}-running, a
% total of \numMedLong{} subjects (see Figure~\ref{fig:rq1-barplot}). To
% reduce noise we did not consider projects with \shortg{}-running test
% suites as we observed that \percentShortSequential{} of those projects
% do not use parallelism; including them would favor sequential
% execution in our analysis.

To extend our initial investigation, we mined several \pomf{} files
must contain one of these keywords that contain parallelization
keywords, namely \CodeIn{forkMode}, \CodeIn{forkCount}, and
\CodeIn{parallel}.  This mining step, however, is not sound as a
matching project may not indicate a project with a valid configuration
for running tests in parallel.  False positive can happen because of
comments, for instance.  To eliminate the cases of false positives and
also to categorize true positive cases, we complemented the initial
mining step with a manual inspection of files.

@@

From the \numProjectsPar{} projects identified above, we investigated
further the \numPomMatchedValid{} build files with parallel settings.
We analyzed the support and distribution of parallel modes from this
subset of projects. To calculate the distribution of parallel modes,
we considered only the presence of the mode in at least one of the
project settings.  Recall that a build file may contain more than one
parallel setting and a project may contain several sub-modules with
build files.  In case the value of a parallel option is resolved
dynamically (\eg, via command-line argument or system variable) we
compute all modes related to the option. For instance, depending on
the value, the \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
Figure~\ref{fig:freqmodes-static} summarizes our findings. \Jbc{Given that we
checked each configuration, we could elaborate how these settings are
used.} \Fix{Missing conclusion: Fork the most used configuration}

>>>>

To extend our initial investigation, we mined several \pomf{} files
from all \numMedLong{} projects classified as the \medg{} and
\longg{}-running.
\Jbc{rework this... $\rightarrow$}To reduce the number of build files
to inspect, we consider only must contain one of these keywords that
contain parallelization keywords, namely \CodeIn{forkMode},
\CodeIn{forkCount}, and \CodeIn{parallel}.  This mining step, however,
is not sound as a matching project may not indicate a project with a
valid configuration for running tests in parallel.  False positive can
happen because of comments, for instance.  To eliminate the cases of
false positives and also to categorize true positive cases, we
complemented the initial mining step with a manual inspection of
files.

@@

\Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
identified above, we investigated further the \numPomMatchedValid{}
build files with parallel settings.  We analyzed the support and
distribution of parallel modes from this subset of projects. To
calculate the distribution of parallel modes, we considered only the
presence of the mode in at least one of the project settings.  Recall
that a build file may contain more than one parallel setting and a
project may contain several sub-modules with build files.  In case the
value of a parallel option is resolved dynamically (\eg, via
command-line argument or system variable) we compute all modes related
to the option. For instance, depending on the value, the
\CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
Figure~\ref{fig:freqmodes-static} summarizes our findings.
\Fix{Missing conclusion: Fork the most used configuration}
